Adaptive group-regularized logistic elastic net regression

### 2019-03-22 docs/manuscript.Rnw
textual changes

	The rest of the paper is structured as follows. We introduce the Bayesian 
	logistic generalised elastic net model in Section
	\ref{sec:model}. In Section \ref{seq:estimation} we derive a variational
	approximation to this model and use this novel approximation in the empirical
	Bayes estimation of multiple, group-specific penalty parameters. In Section
	\ref{sec:simulations} we compare the method in a simulation study. In Sections
	\ref{sec:colorectal} and \ref{sec:lymphnode}, we demonstrate the approach in 
	two data sets. In Section \ref{sec:discussion} 
	we conclude by both discussing some differences and
	parallels between the proposed method, termed \texttt{gren}, and other methods
	in the literature.

@@

	\section{Estimation}\label{seq:estimation}
	\subsection{Empirical Bayes}\label{seq:empiricalbayes}
	If the penalty parameters are known, estimation of the frequentist elastic net
	model parameters or finding the posterior of the generalized elastic net model
	is feasible with small adjustments of the available algorithms 
	\cite[]{friedman_regularization_2010,zou_regularization_2005} or MCMC samplers
	\cite[]{li_bayesian_2010}. Determining these penalty parameters, however, is 
	not straightforward.

@@

	\subsection{Empirical-variational Bayes}\label{seq:empvarbayes}
	Variational Bayes was shown to underestimate the posterior variance of the 
	parameters, both numerically and theoretically, in several settings 
	\cite[]{rue_approximate_2009,consonni_mean-field_2007,bishop_pattern_2006,
	wang_inadequacy_2005}. This coincides with our experience that the global 
	penalty parameters $\lambda_1$ and $\lambda_2$ tend to be overestimated. To 
	prevent overestimation we use the parametrisation of the elastic net in 
	\cite{friedman_regularization_2010} as introduced in Section 
	\ref{seq:empiricalbayes}: we fix $\alpha$ and estimate $\lambda$ by 
	cross-validation of the regular elastic net model, such that the overall 
	penalisation is determined by cross-validation of only $\lambda$. By combining
	cross-validation of the global penalty parameter $\lambda$ with empirical 
	Bayes estimation of the penalty multipliers $\blambda' = \begin{bmatrix} 
	\lambda'_1 & \cdots & \lambda'_G \end{bmatrix} \tr$, the estimation is more 
	robust to underestimation of the variational posterior variances. The 
	remaining issue is the choice of $\alpha$. \cite{hastie_glmnet_2016} recommend
	to either fix $\alpha$ \textit{a priori}, or compare the results for several 
	choices of $\alpha$. We recommend the latter.

@@

	As shortly touched upon in Section \ref{seq:empiricalbayes}, frequentist 
	feature selection is trivial after estimation of the penalty multipliers. We 
	simply plug the estimated penalty parameters into some frequentist elastic net
	algorithm that allows for differential penalization. In our own package 
	\texttt{gren}, we use the \texttt{R}-package \texttt{glmnet} 
	\cite[]{friedman_regularization_2010}. In the frequentist elastic net, feature
	selection is then done automatically. Furthermore, to select a specific number
	of features, we simply adjust the global $\lambda$ until we select the desired
	number of features.

	\section{Simulations}\label{sec:simulations}
	To assess variable selection and predictive performance we conducted a 
	simulation study in which we compared \texttt{gren} to the regular elastic 
	net and ridge models, \texttt{GRridge} \cite[]{van_de_wiel_better_2016}, 
	sparse group lasso (\texttt{SGL}) \cite[]{simon_sparse-group_2013}, 
	composite mimimax concave penalty (\texttt{cMCP}) 
	\cite[]{breheny_penalized_2009}, and the group exponential lasso 
	(\texttt{gel}) \cite[]{breheny_group_2015}. \texttt{GRridge} is similar to 
	\texttt{gren} in the sense that it estimates group-specific penalty 
	multipliers. The two main differences with \texttt{gren} are (i) the absence 
	of an $L_1$-norm penalty and (ii) the estimation procedure. The other methods 
	are extensions of the group lasso and not adaptive on the group level. 
	However, in contrast to the original group lasso,
	they select single features, instead of just whole groups.

	For the regular elastic net, \texttt{gren}, \texttt{SGL}, \texttt{cMCP}, 
	and \texttt{gel}, we fix $\alpha \in \{0.05, 0.5, 0.95 \}$. In \texttt{gren}
	and the elastic net, $\alpha$ determines the proportion of $L_1$-norm penalty,
	such that the first setting closely resembles the ridge setting, 
	where $\alpha=0$, while the third setting is similar to the lasso with 
	$\alpha=1$. In \texttt{SGL}, \texttt{cMCP}, and \texttt{gel}, $\alpha$
	determines the ratio of group-level penalization ($\alpha=0$) to 
	feature level ($\alpha=1$) penalization. For the methods that do 
	automatic feature selection, we estimate 
	the models for a range of model sizes.

	We simulated data according to five different scenarios:
	\begin{enumerate}
		\item differential signal between the groups and uniformly distributed model
		parameters,
		\item a large number of small groups of features,
		\item no differential signal between the groups, but strong correlations 
		within groups of features,
		\item differential signal between the groups and heavy-tailed distributed 
		model parameters, and
		\item a very sparse setting with no signal in some of the groups.
	\end{enumerate}
	Full descriptions of the scenarios are given in Section 
	\ref{sm-sec:simulations} of 
	the SM. In the first scenario, the distribution of model parameters is far
	from the assumed ridge/elastic net/lasso distributions, so we expect
	all methods to underperform. In the second scenario, which is similar to
	the simulations presented in the original group lasso paper 
	\cite[]{yuan_model_2006}, we expect \texttt{gren}
	and \texttt{GRridge} to overfit due to the large number of hyperparameters to 
	estimate, while we expect the other methods to perform better, due to a
	lack of overfitting. In scenario three, we expect all methods to underperform
	due to the high correlations between the features. The fourth 
	scenario is conjectured to yield a better \texttt{gren} performance, since
	\texttt{gren} assumes a heavier-tailed distribution and is designed to 
	incorporate a differential signal between
	the groups. Scenario five is expected to yield a bad performance for all 
	methods, because of the sparse truth and lack of differential 
	signal.

	In all scenarios we created a training set of $n=100$ samples to estimate the 
	models and a test set of $n_{\text{test}}=1000$ samples to compute 
	the performance measures. The features $\x_i$, $i=1, \dots, n$, are taken 
	from a $p$-dimensional zero-centred Gaussian distribution, where we set 
	$p=1000$. We varied the covariance matrix of the features and simulation of 
	the model parameters $\beta_j$, $j=1, \dots, p$ between the
	scenarios (see SM Section [! section ref here] for the exact 
	parametrisations). We 
	simulated the outcomes $y_i$, $i=1, \dots, n$, from a binary logistic model: 
	$y_i \sim \mathcal{B}(1, \expit (\x_i \tr \bbeta))$. To mitigate the influence
	of random variation, we repeated each scenario 100 times 
	and report estimated penalty parameters and predictive performance measures 
	area under the receiver operator curve (AUC) and Brier skill score (BSS) in 
	Table [! table ref here].

@@

	Additional results and performance measures are presented in Section 
	\ref{sm-sec:simulations} of the SM.

@@

	Although our method can be considered weakly adaptive and is essentially 
	a reweighted elastic net, it is different from 
	the adaptive lasso \cite[]{van_de_geer_adaptive_2011,huang_adaptive_2008,
	zhang_adaptive_2007,zou_adaptive_2006} and adaptive elastic net 
	\cite[]{zou_adaptive_2009} in the sense that it adapts to external information
	rather than to the primary data. It also differs in the scale of adaptation: 
	in the adaptive lasso and elastic net the adaptive weights are feature 
	specific, while in our case they are estimated on the group level, rendering
	the adaptation more robust. As can be seen from both the simulations in 
	Section \ref{sec:simulations} and the applications to different outcomes 
	(prognostic or diagnostic) and marker types 
	(RNAseq, microRNAs, or metabolomics) in Sections \ref{sec:colorectal}--
	\ref{sec:lymphnode}, and SM Sections \ref{sm-sec:colorectal}--
	\ref{sm-sec:cervical}, adaptation to 
	external data may be beneficial for prediction and feature selection. 
	We believe that this is due to the `borrowing of information' effect: 
	estimates of feature effects that behave similarly are shrunken similarly, 
	yielding overall, better estimates.

	A common criticism of the lasso (and elastic net) is its instability of 
	feature 
	selection: different data instances lead to different sets of selected
	features. We investigated the stability of selection on the data from Section
	\ref{sec:colorectal}. To that end we created several bootstrap samples from 
	the original data and calculated the sizes of all intersections of selected
	features. We compared \texttt{gren} to the 
	regular elastic net and found that the inclusion of extra information
	increased the selection stability (see SM Section \ref{sm-sec:colorectal}). 
	In addition, we investigated 
	the variance and bias in penalty multiplier estimation by examining the
	distribution
	of estimated penalty parameters from 100 random partitionings of the features
  (see SM Section \ref{sm-sec:colorectal}). We found that the penalty parameters
  tend to cluster around one, as expected for an unbiased estimation method.

	As touched upon in Section \ref{sec:introduction}, another obvious 
	comparison is to the group lasso \cite[]{meier_group_2008,
	yuan_model_2006} and its extensions. Although the group lasso is similar in 
	the sense that it shrinks on the 
	group level, it is built upon an entirely different philosophy: 
	its intended application is to small interpretable groups of features, like, 
	for example, dummies of a categorical variable. Another difference between 
	\texttt{gren} and the group lasso is the number of penalty parameters. 
	\texttt{gren} estimates one parameter per group, while the group lasso
	estimates one overall penalty parameter; it is thereby less flexible in 
	differential shrinkage of the parameters. In addition, we show in our 
	simulations and data applications that \texttt{gren} is competitive and often
	even superior to (extensions of) the group lasso.

	A possible weak point of the proposed method is the double EM loop. The double
	loop increases the chance of ending up in a local optimum. In the application
	discussed above we investigated the occurrence of multiple optima, but never
	encountered them. This does not guarantee that local optima do not occur, but 
	it provides some evidence that local optima are not ubiquitous. Local optima 
	can often be avoided by an informed choice of starting values. In our 
	experience, reasonable starting values are obtained by running a 
	group-regularized ridge regression and using the estimated penalty multipliers
	as starting values for \texttt{gren}. Alternatively, a skeptical user may set 
	the starting values for all penalty multipliers to one, thereby starting from
	the regular elastic net and adaptively adjusting the penalty parameters to a
	group-regularized model.

<<>>=
bench1 <- read.table("results/micrornaseq_colorectal_cancer_bench1.csv", 
                     stringsAsFactors=FALSE)
bench2 <- read.table("results/rnaseq_lymph_node_metastasis_bench1.csv", 
                     stringsAsFactors=FALSE)
times1 <- round(bench1$time*10^(-9), 2)
times2 <- round(bench2$time*10^(-9), 2)
session <- gsub("_", ".", devtools::session_info()$platform$system)
@
  The double EM loop runs the danger of excessive computation time. We have   
  compared computation times to the
  other methods introduced in Sections \ref{sec:colorectal}--
  \ref{sec:lymphnode}. All timings were obtained on a Macbook 
  Pro 2016 running \Sexpr{session}. 
  The timings of \texttt{gren} are competitive. On the colorectal cancer example
  we achieved the following times:
  \Sexpr{times1[c(1:3)]} seconds, with $\alpha \in \{ 0.05, 0.5, 0.95 \}$, 
  respectively. \texttt{GRridge} is 
  slightly faster with \Sexpr{times1[4]} seconds, while \texttt{SGL} was slightly
  slower: \Sexpr{times1[c(5:7)]} seconds, with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$.
  \texttt{cMCP} (\Sexpr{times1[c(8:10)]} seconds) and \texttt{gel} 
  (\Sexpr{times1[c(11:13)]} seconds) are faster than \texttt{gren}. 
  The results for the lymph node cancer example are similar. \texttt{gren} 
  achieved 
  \Sexpr{times2[c(1:3)]} seconds, with $\alpha \in \{ 0.05, 0.5, 0.95 \}$, 
  respectively.
  \texttt{GRridge} was slightly faster with \Sexpr{times2[4]} seconds, 
  while \texttt{SGL} was slightly slower: \Sexpr{times2[c(5:7)]} seconds, with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$.
  \texttt{cMCP} (\Sexpr{times2[c(14:16)]} seconds) and \texttt{gel} 
  (\Sexpr{times2[c(17:19)]} seconds) are again faster than \texttt{gren}. 
  We note that a considerable speedup may be achieved by iterating between 
  single EB and single VB updates, instead of running the VB EM 
  until convergence. This works in practice, because an EM tends to take a few 
  initial large steps towards the optimum, followed by a series of smaller 
  steps. We argue that the first few iterations of the VB EM render the 
  approximate expectation in \ref{eq:approximatedloglikelihood}
  accurate enough for a 
  reliable EB step. This approach is often used in more 
  computational disciplines, where the problem is viewed as purely algorithmic 
  and the EB and VB iterations are interpreted as optimisation steps along the 
  gradient in the larger combined model- and hyper-parameters space.

@@

	\section*{Session info}
<<r session-info, eval=TRUE, echo=TRUE, tidy=TRUE>>=
devtools::session_info()
@

>>>>

	The rest of the paper is structured as follows. We introduce the Bayesian 
	logistic generalised elastic net model in Section
	\ref{sec:model}. In Section \ref{sec:estimation} we derive a variational
	approximation to this model and use this novel approximation in the empirical
	Bayes estimation of multiple, group-specific penalty parameters. In Section
	\ref{sec:simulations} we compare the method in a simulation study. In Sections
	\ref{sec:colorectal} and \ref{sec:lymphnode}, we demonstrate the approach in 
	two data sets. In Section \ref{sec:discussion} 
	we conclude by both discussing some differences and
	parallels between the proposed method, termed \texttt{gren}, and other methods
	in the literature.

@@

	\section{Estimation}\label{sec:estimation}
	\subsection{Empirical Bayes}\label{sec:empiricalbayes}
	If the penalty parameters are known, estimation of the frequentist elastic net
	model parameters or finding the posterior of the generalized elastic net model
	is feasible with small adjustments of the available algorithms 
	\cite[]{friedman_regularization_2010,zou_regularization_2005} or MCMC samplers
	\cite[]{li_bayesian_2010}. Determining these penalty parameters, however, is 
	not straightforward.

@@

	\subsection{Empirical-variational Bayes}\label{sec:empvarbayes}
	Variational Bayes was shown to underestimate the posterior variance of the 
	parameters, both numerically and theoretically, in several settings 
	\cite[]{rue_approximate_2009,consonni_mean-field_2007,bishop_pattern_2006,
	wang_inadequacy_2005}. This coincides with our experience that the global 
	penalty parameters $\lambda_1$ and $\lambda_2$ tend to be overestimated. To 
	prevent overestimation we use the parametrisation of the elastic net in 
	\cite{friedman_regularization_2010} as introduced in Section 
	\ref{sec:empiricalbayes}: we fix $\alpha$ and estimate $\lambda$ by 
	cross-validation of the regular elastic net model, such that the overall 
	penalisation is determined by cross-validation of only $\lambda$. By combining
	cross-validation of the global penalty parameter $\lambda$ with empirical 
	Bayes estimation of the penalty multipliers $\blambda' = \begin{bmatrix} 
	\lambda'_1 & \cdots & \lambda'_G \end{bmatrix} \tr$, the estimation is more 
	robust to underestimation of the variational posterior variances. The 
	remaining issue is the choice of $\alpha$. \cite{hastie_glmnet_2016} recommend
	to either fix $\alpha$ \textit{a priori}, or compare the results for several 
	choices of $\alpha$. We recommend the latter.

@@

	As shortly touched upon in Section \ref{sec:empiricalbayes}, frequentist 
	feature selection is trivial after estimation of the penalty multipliers. We 
	simply plug the estimated penalty parameters into some frequentist elastic net
	algorithm that allows for differential penalization. In our own package 
	\texttt{gren}, we use the \texttt{R}-package \texttt{glmnet} 
	\cite[]{friedman_regularization_2010}. In the frequentist elastic net, feature
	selection is then done automatically. Furthermore, to select a specific number
	of features, we simply adjust the global $\lambda$ until we select the desired
	number of features.

	\section{Simulations}\label{sec:simulations}
	To assess classification and variable selection performance we conducted a 
	simulation study in which we compared \texttt{gren} to the regular elastic 
	net and ridge models, \texttt{GRridge} \cite[]{van_de_wiel_better_2016}, 
	sparse group lasso (\texttt{SGL}) \cite[]{simon_sparse-group_2013}, 
	composite mimimax concave penalty (\texttt{cMCP}) 
	\cite[]{breheny_penalized_2009}, and the group exponential lasso 
	(\texttt{gel}) \cite[]{breheny_group_2015}. \texttt{GRridge} is similar to 
	\texttt{gren} in the sense that it estimates group-specific penalty 
	multipliers. The two main differences with \texttt{gren} are (i) the absence 
	of an $L_1$-norm penalty and (ii) the estimation procedure. The other methods 
	are extensions of the group lasso and not adaptive on the group level. 
	However, in contrast to the original group lasso,
	they select single features, instead of just whole groups.

	For the regular elastic net, \texttt{gren}, \texttt{SGL}, \texttt{cMCP}, 
	and \texttt{gel}, we fix $\alpha \in \{0.05, 0.5, 0.95 \}$. In \texttt{gren}
	and the elastic net, $\alpha$ determines the proportion of $L_1$-norm penalty,
	such that the first setting closely resembles the ridge setting, 
	where $\alpha=0$, while the third setting is similar to the lasso with 
	$\alpha=1$. In \texttt{SGL}, \texttt{cMCP}, and \texttt{gel}, $\alpha$
	determines the ratio of group-level penalization ($\alpha=0$) to 
	feature level ($\alpha=1$) penalization. For the methods that do 
	automatic feature selection, we estimate models for a range of model sizes.

	We simulated data according to five different scenarios:
	\begin{enumerate}
		\item differential signal between the groups and uniformly distributed model
		parameters,
		\item a large number of small groups of features,
		\item no differential signal between the groups, but strong correlations 
		within groups of features,
		\item differential signal between the groups and heavy-tailed distributed 
		model parameters, and
		\item a very sparse setting with no signal in some of the groups.
	\end{enumerate}
	Full descriptions of the scenarios are given in Section 
	\ref{sm-sec:simulations} of 
	the SM. In the first scenario, the distribution of model parameters is far
	from the assumed ridge/elastic net/lasso distributions, so we expect
	all methods to underperform. In the second scenario, which is similar to
	the simulations presented in the original group lasso paper 
	\cite[]{yuan_model_2006}, we expect \texttt{gren}
	and \texttt{GRridge} to overfit due to the large number of hyperparameters to 
	estimate. The group lasso extensions are expected to perform better: they 
	estimate just one penalty parameter, so are less sensitive to overfitting.
	In scenario three, we expect all methods to underperform
	due to the high correlations between the features. The fourth 
	scenario is expected to yield a better \texttt{gren} performance, since
	\texttt{gren} assumes a heavier-tailed distribution and is designed to 
	detect differential signal between
	the groups. Scenario five is expected to yield a bad performance for all 
	methods, because of the sparse truth and lack of differential 
	signal.

	In all scenarios we created a training set of $n=100$ samples to estimate the 
	models and a test set of $n_{\text{test}}=1000$ samples to compute 
	the performance measures. The features $\x_i$, $i=1, \dots, n$, are taken 
	from a $p$-dimensional zero-centred Gaussian distribution, where we set 
	$p=900$ in scenario 2 and $p=1000$ in the other scenarios. We varied the 
	covariance matrix of the features and simulation of 
	the model parameters $\beta_j$, $j=1, \dots, p$ between the
	scenarios (see SM Section \ref{sm-sec:simulations} for the exact 
	parametrisations). We 
	simulated the outcomes $y_i$, $i=1, \dots, n$, from a binary logistic model: 
	$y_i \sim \mathcal{B}(1, \expit (\x_i \tr \bbeta))$. To mitigate the influence
	of random variation, we repeated each scenario 100 times 
	and report predictive performance measures 
	area under the receiver operator curve (AUC) and Brier skill score (BSS) in 
	Figures \ref{fig:lines_simulations_res1_auc_briers}--[! figure refs here]. 
	Additional results and performance measures are presented in Section 
	\ref{sm-sec:simulations} of the SM.

@@

@@

	Although our method is essentially a reweighted elastic net and can be
	considered weakly adaptive, it is different from 
	the adaptive lasso \cite[]{van_de_geer_adaptive_2011,huang_adaptive_2008,
	zhang_adaptive_2007,zou_adaptive_2006} and adaptive elastic net 
	\cite[]{zou_adaptive_2009} in the sense that it adapts to external information
	rather than to the primary data. It also differs in the scale of adaptation: 
	in the adaptive lasso and elastic net the adaptive weights are feature 
	specific, while in our case they are estimated on the group level, rendering
	the adaptation more robust. As can be seen from both the simulations in 
	Section \ref{sec:simulations} and the applications to different outcomes 
	(prognostic or diagnostic) and marker types 
	(RNAseq, microRNAs, or metabolomics) in Sections \ref{sec:colorectal}--
	\ref{sec:lymphnode}, and SM Sections \ref{sm-sec:colorectal}--
	\ref{sm-sec:cervical}, adaptation to 
	external data may be beneficial for prediction and feature selection. 
	We believe that this is due to the `borrowing of information' effect: 
	estimates of feature effects that behave similarly are shrunken similarly, 
	yielding overall, better estimates.

	As touched upon in Section \ref{sec:introduction}, an obvious 
	comparison is to the group lasso \cite[]{meier_group_2008,
	yuan_model_2006} and its extensions. Although the group lasso is similar in 
	the sense that it shrinks on the 
	group level, it is built upon an entirely different philosophy: 
	its intended application is to small interpretable groups of features, like, 
	for example, dummies of a categorical variable. Another difference between 
	\texttt{gren} and the group lasso is the number of penalty parameters. 
	\texttt{gren} estimates one parameter per group, while the group lasso
	estimates one overall penalty parameter; it is thereby less flexible in 
	differential shrinkage of the parameters. In addition, we show in our 
	simulations and data applications that \texttt{gren} is competitive and often
	superior to (extensions of) the group lasso.

	A common criticism of the lasso (and elastic net) is its instability of 
	feature 
	selection: different data instances lead to different sets of selected
	features. We investigated the stability of selection on the data from Section
	\ref{sec:colorectal}. To that end we created several bootstrap samples from 
	the original data and calculated the sizes of all intersections of selected
	features. We compared \texttt{gren} to the 
	regular elastic net and found that the inclusion of extra information
	increased the selection stability (see SM Section \ref{sm-sec:colorectal}). 
	In addition, we investigated 
	the bias and variance of the penalty multipliers by examination of the
	distribution of estimated penalty parameters from 100 random partitionings 
	of the features
  (see SM Section \ref{sm-sec:colorectal}). We found that the penalty parameters
  tend to cluster around one, as expected for an unbiased estimation method, and
  that the variance of the penalty multipliers is less than for the similar
  \texttt{GRridge} method.

	A possible weak point of the proposed method is the double EM loop. The double
	loop increases the chance of ending up in a local optimum. In the applications
	discussed in Sections \ref{sec:colorectal}--
	\ref{sec:lymphnode}, and SM Sections \ref{sm-sec:colorectal}--
	\ref{sm-sec:cervical}, we investigated the occurrence of multiple optima, 
	but never encountered them. This does not guarantee that local optima do not
	occur, but 
	it provides some evidence that local optima are not ubiquitous. In any case,
	bad local optima can often be avoided by an informed choice of starting 
	values. In our 
	experience, reasonable starting values are obtained by running a 
	group-regularized ridge regression and using the estimated penalty multipliers
	as starting values for \texttt{gren}. Alternatively, a skeptical user may set 
	the starting values for all penalty multipliers to one, thereby starting from
	the regular elastic net and adaptively adjusting the penalty parameters to a
	group-regularized model. The latter is the default approach in our \texttt{R}
	package

<<>>=
bench1 <- read.table("results/micrornaseq_colorectal_cancer_bench1.csv", 
                     stringsAsFactors=FALSE)
bench2 <- read.table("results/rnaseq_lymph_node_metastasis_bench1.csv", 
                     stringsAsFactors=FALSE)
times1 <- round(bench1$time*10^(-9), 2)
times2 <- round(bench2$time*10^(-9), 2)
session <- gsub("_", ".", devtools::session_info()$platform$system)
@
  The double EM loop runs the danger of excessive computation time. We have   
  compared computation times to the
  other methods introduced in Sections \ref{sec:colorectal}--
  \ref{sec:lymphnode}. All timings were obtained on a Macbook 
  Pro 2016 running \Sexpr{session}. 
  The timings of \texttt{gren} are competitive. On the colorectal cancer example
  we achieved the following times:
  \Sexpr{times1[c(1:3)]} seconds, with $\alpha \in \{ 0.05, 0.5, 0.95 \}$, 
  respectively. \texttt{GRridge} is 
  slightly faster with \Sexpr{times1[4]} seconds, while \texttt{SGL} was slightly
  slower: \Sexpr{times1[c(5:7)]} seconds, with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$.
  \texttt{cMCP} (\Sexpr{times1[c(8:10)]} seconds) and \texttt{gel} 
  (\Sexpr{times1[c(11:13)]} seconds) are faster than \texttt{gren}. 
  The results for the lymph node cancer example are similar. \texttt{gren} 
  achieved 
  \Sexpr{times2[c(1:3)]} seconds, with $\alpha \in \{ 0.05, 0.5, 0.95 \}$, 
  respectively.
  \texttt{GRridge} was slightly faster with \Sexpr{times2[4]} seconds, 
  while \texttt{SGL} was slightly slower: \Sexpr{times2[c(5:7)]} seconds, with 
  $\alpha \in \{ 0.05, 0.5, 0.95 \}$.
  \texttt{cMCP} (\Sexpr{times2[c(14:16)]} seconds) and \texttt{gel} 
  (\Sexpr{times2[c(17:19)]} seconds) are again faster than \texttt{gren}. 
  We note that a considerable speedup may be achieved by iterating between 
  single EB and single VB updates, instead of running the VB EM 
  until convergence. This works in practice, because an EM tends to take a few 
  initial large steps towards the optimum, followed by a series of smaller 
  steps. We argue that the first few iterations of the VB EM render the 
  approximate expectation in \ref{eq:approximatedloglikelihood}
  accurate enough for a 
  reliable EB step.

@@

	\section*{Session info}

<<r session-info, eval=TRUE, echo=TRUE, tidy=TRUE>>=
devtools::session_info()
@
